Improving content discovery through combining linked data and data mining techniques

### 2015-12-22 report/report.tex
Started architecture

\begin{sidewaysfigure}[p]
  \begin{center}
    \begin{dot2tex}[dot,options=-t math,autosize,pgf]
      digraph g {
        rankdir=LR;

@@

        RDFp -> Features [label="generate"];
      }
    \end{dot2tex}
  \end{center}
  \caption{\label{fig:maximal-pipeline}Maximal Data Pipeline}
\end{sidewaysfigure}

>>>>

\begin{sidewaysfigure}[p]
  \begin{center}
    \begin{dot2tex}[dot,options=-t math,autosize,pgf,scale=0.9]
      digraph g {
        rankdir=LR;

@@

        RDFp -> Features [label="\text{content\_?p\_?v}"];
        RDFp -> Features [label="\text{content\_?p1\_?p2\_?v}"];
      }
    \end{dot2tex}
  \end{center}
  \caption{\label{fig:maximal-pipeline}Maximal Data Pipeline}
\end{sidewaysfigure}

The goal of this work is to evaluate how the quality of unsupervised clustering
changes with respect to enabling different combinations of the maximal
data pipeline. In the next section, some of the technical architecture of this
pipeline is outlined and the next chapter will cover how the overall system is
then implemented.
